\documentclass[11pt,a4paper,sans]{article}
\usepackage{mycvstyle}
\addbibresource{papers.bib}

\hypersetup{
    hidelinks,
    pdftitle={Publication List - Bastien Carreres},
    pdfauthor={Bastien Carreres}
}                          % Links and PDF metadata


%%%%%%%%%%%%%%%%%%%%%%%%%
% DOCUMENT
%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}

\begin{center}
    {\Huge\bfseries List of Publications}
    
    \vspace{10pt}
    {\LARGE \color{cvblue} \bfseries Bastien Carreres} 

\end{center}

\nocite{*}

\setupcvsections

\section{Publications}
\printbibliography[heading=myheading, title=Publications as first author, keyword={FirstAuth}]
\printbibliography[heading=myheading,title=Publications with significant contribution, keyword={SignContrib}]
\printbibliography[heading=myheading,title=Publications as co-author, keyword={Other}]

\section{Talks}
\begin{enumerate}
  \setlength\itemsep{1em}
   \item Jan. 2026 - \href{https://bastiencarreres.com/talks/CPPM-2026-12-01/index.html}{\textbf{SNe Ia growth-rate measurements with Rubin-LSST simulations: intrinsic scatter systematics}} at \textit{CPPM Renoir science meeting}, Marseille, France
  \item Nov. 2025 -- \href{https://bastiencarreres.com/talks/descmcp-2025-11-12/DESC_Project_Announcement_%20Constraining_Structure_Growth_and_Modified_Gravity_Using_LSST_lowz_SNe_Ia_PVs_and_Weak_Lensing.pdf}{\textbf{DESC Project announcement: Constraining Structure Growth and Modified Gravity Using LSST low-z SN Ia PVs and Weak Lensing}} at \textit{DESC-MCP meeting}, online
  \item Sept. 2025 -- \href{https://bastiencarreres.com/talks/desc-pv-workshop-2025-09-22/DESCPV-2025-09-22.pdf}{\textbf{Status of PV cosmology in LSST-DESC}} at \textit{DESC workshop on cosmology with peculiar velocities}, Marseille, France
   \item Jul. 2025 - \href{https://bastiencarreres.com/talks/cosmiclighthouse-2025-07-02/index.html}{\textbf{SNe Ia growth-rate measurements with Rubin-LSST simulations: intrinsic scatter systematics}} at \textit{Cosmic Lighthouses 2025}, Cambridge, UK
  \item Feb. 2025 -- \href{https://bastiencarreres.github.io/talks/cosmicflows-2025-02-03/CF2025_GalGrpSN_250203.pdf}{\textbf{Improving SN Ia Hubble residual scatter with galaxy groups}} at \textit{CosmicFlows 2025}, Brisbane, Australia
  \item Mar. 2025 -- \href{https://bastiencarreres.github.io/talks/clermontferrand-2025-03-19/index.html}{\textbf{SNe Ia growth-rate measurements with Rubin-LSST simulations~: intrinsic scatter systematics}} at \textit{SN Ia cosmology group of LPCA}, online
  \item Feb. 2025 -- \href{https://bastiencarreres.github.io/talks/cosmicflows-2025-02-06/index.html}{\textbf{SNe Ia growth-rate measurements with Rubin-LSST simulations~: intrinsic scatter systematics}} at \textit{CosmicFlows 2025}, Brisbane, Australia
  \item Oct. 2024 -- \href{https://bastiencarreres.github.io/talks/desctd-2024-10-15/DESC_PV_BBC_project.pdf}{\textbf{DESC Project announcement: Measurement of the growth-rate of structures using SN Ia PVs in the BBC framework}} at \textit{DESC-TD biweekly meeting}, online
  \item Sept. 2023 -- \href{https://indico.in2p3.fr/event/30615/contributions/128392/attachments/79574/116616/Possible%20impacts%20of%20velocities%20on%20the%20fit%20of%20the%20HD.pdf}{\textbf{Possible velocity systematic on the Hubble diagram fit}} at \textit{ZTF France}, LPC, Clermont-Ferrand, France 
  \item Aug. 2023 -- \href{https://bastiencarreres.github.io/talks/DESCTD-2023-03-28/index.html}{\textbf{$\boldsymbol{f\sigma_8}$ measurement with type Ia supernovae}} at \textit{DESC-TD biweekly meeting}, online 
  \item May 2023 --  \href{https://bastiencarreres.github.io/talks/duke-2023-04-20/index.html}{\textbf{Growth-rate measurement with type Ia supernovae}} at the \textit{Duke cosmology group’ seminar} 
  \item Nov. 2022 --  \href{https://indico.in2p3.fr/event/27399/contributions/116473/attachments/74014/106473/ADE_2022_bc.pdf}{\textbf{Cosmology with the growth rate using type Ia supernovae}} at \textit{Action Dark Energy 2022}, Marseille, France 
  \item May 2022 -- \href{https://indico.in2p3.fr/event/26455/contributions/109704/attachments/70514/100017/f%CF%838%20with%20SN%20Ia%20-%20LSST%20france.pdf}{\textbf{Measuring $\boldsymbol{f\sigma_8}$ with the ZTF SN Ia sample}} at \textit{Rubin-LSST France 2022}, LAPP, Annecy, France 
  \item May 2022 -- \href{https://indico.in2p3.fr/event/26793/contributions/109542/attachments/70416/99834/f%CF%838%20with%20SN%20Ia%20-%20ZTF%20Paris.pdf}{\textbf{Measuring $\boldsymbol{f\sigma_8}$ with the ZTF SN Ia sample}} at \textit{ZTF spring meeting}, LPNHE, Paris, France
  \item June 2021 -- \href{https://indico.in2p3.fr/event/23494/contributions/95032/attachments/64400/89320/Pre%CC%81sentation_lsst_france_final.pdf}{\textbf{Peculiar velocities with Type Ia Supernovae}} at \textit{Rubin-LSST France 2021}, LPSC, Grenoble, France
\end{enumerate}

\section{Posters}
\begin{enumerate}
  \item 2022 - \href{https://bastiencarreres.github.io/talks/Poster_Moriond_Chicago.pdf}{\textbf{Cosmology with the growth rate of structures using type Ia supernovae}} at \textit{DESC Summer Meeting 2022}, University of Chicago
  \item 2022 - \href{https://bastiencarreres.github.io/talks/Poster_Moriond_Chicago.pdf}{\textbf{Cosmology with the growth rate of structures using type Ia supernovae}} + \href{https://moriond.in2p3.fr/download/proceedings_cosmology_2022.pdf}{\textbf{Proceedings}} at \textit{Rencontres de Moriond}
\end{enumerate}

\end{document}
